The \raveon\ catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2017-03-14 article/unrave.tex
typo

% A magic, bad, hack.
\noindent{}$^{1}${Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK} \\
$^{2}${Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA} \\
$^{3}${Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY 10003, USA} \\
$^{4}${Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA} \\
$^{5}${Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany} \\
$^{6}$Leibniz-Institut für Astrophysik Potsdam (AIP), An der Sternwarte 16, D-14482 Potsdam, Germany \\
$^{7}${University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia} \\
$^{8}${Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, ACT 2611, Australia} \\

$^{9}${Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, RH5 6NT, UK} \\
$^{10}${Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l'Universit\'e, F-67000 Strasbourg, France} \\
$^{11}${Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia} \\
$^{12}${E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom} \\
$^{13}${Astronomisches Rechen-Institut, Zentrum f\"ur Astronomie der Universit\"at Heidelberg, M\"onchhofstr.\ 12--14, 69120 Heidelberg, Germany} \\
$^{14}${Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands} \\
$^{15}${INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy} \\
$^{16}${Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2} \\
$^{17}${Senior CIfAR Fellow} \\
$^{18}${Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia} \\
$^{19}${Western Sydney University, Penrith South DC, NSW 1797} \\
$^{20}${Johns Hopkins University, Baltimore, MD, USA} \\

>>>>

% A magic, bad, hack.
\noindent{}$^{1}${Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK} \\
$^{2}${Simons Center for Data Analysis, 160 Fifth Avenue, 7th floor, New York, NY 10010, USA} \\
$^{3}${Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY 10003, USA} \\
$^{4}${Center for Data Science, New York University, 726 Broadway, 7th floor, New York, NY 10003, USA} \\
$^{5}${Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany} \\
$^{6}${Leibniz-Institut f\"ur Astrophysik Potsdam (AIP), An der Sternwarte 16, D-14482 Potsdam, Germany} \\
$^{7}${University of Ljubljana, Faculty of Mathematics and Physics, Jadranska 19, 1000 Ljubljana, Slovenia} \\
$^{8}${Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, ACT 2611, Australia} \\
$^{9}${Mullard Space Science Laboratory, University College London, Holmbury St Mary, Dorking, RH5 6NT, UK} \\
$^{10}${Observatoire astronomique de Strasbourg, Universit\'e de Strasbourg, CNRS, UMR 7550, 11 rue de l'Universit\'e, F-67000 Strasbourg, France} \\
$^{11}${Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia} \\
$^{12}${E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom} \\
$^{13}${Astronomisches Rechen-Institut, Zentrum f\"ur Astronomie der Universit\"at Heidelberg, M\"onchhofstr.\ 12--14, 69120 Heidelberg, Germany} \\
$^{14}${Kapteyn Astronomical Institute, University of Groningen, P.O. Box 800, 9700 AV Groningen, The Netherlands} \\
$^{15}${INAF Astronomical Observatory of Padova, 36012 Asiago (VI), Italy} \\
$^{16}${Department of Physics and Astronomy, University of Victoria, Victoria, BC, Canada V8P 5C2} \\
$^{17}${Senior CIfAR Fellow} \\
$^{18}${Department of Physics and Astronomy, Macquarie University, Sydney, NSW 2109, Australia} \\
$^{19}${Western Sydney University, Penrith South DC, NSW 1797} \\
$^{20}${Johns Hopkins University, Baltimore, MD, USA} \\
